---
title: "EMA"
author: "Alexis Rangel"
date: "2023-05-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

- Cargamos el mejor modelo y el conjunto de datos Train y Test para hacer análisis exploratorio del modelo
```{r, carga del modelo, echo=True}
load("../models/Modelo_1.RData")
load("../brief/DatosParaProyecto.RData")
Train = filter(Train, "Purpose" != "renewable_energy")
```


Explanatory Model Analysis for models is whats Exploratory Data Analysis is for Data

Model agnostic approach
relationship between the input and the output
level explanations vs global explanations
```{r}
library(tidyverse)
library(DALEX)
```

```{r}
Train$Term = as.factor(Train$Term)
Train$Years.in.current.job = as.factor(Train$Years.in.current.job)
Train$Home.Ownership = as.factor(Train$Home.Ownership)
Train$Purpose = tolower(Train$Purpose)
Train$Purpose = as.factor(Train$Purpose)
Train$Loan.Status = ifelse(Train$Loan.Status  == "Fully Paid", 1, 0)
class(Train$Loan.Status)
```



Explaining the model

```{r}
modelo_1_1_explained = explain(
                        modelo_1_1,
                        data = Train,
                        y = Train$Loan.Status,
                        label = "Logistic Regression"
                      )
class(modelo_1_1_explained)
```

Explicaciones desde la libreria DALEX:

```{r}
single_observation = Train[sample(1:nrow(Train), 1), ]

modelo_1_1_explained %>% predict(single_observation)
```
 
```{r}
#single_observation = Train[sample(1:nrow(Train), 1), ]
single_observation = Train[8972, ]
modelo_1_1_explained %>% predict(single_observation)
modelo_1_1_explained %>% predict_parts(new_observation = single_observation) %>% plot(title="Break-Down for single obs with Fully Paid response")
```

Identificando el charged off (id = 11434)

```{r}
modelo_1_1_explained %>% predict_profile(new_observation = select(single_observation, -c('ID'))) %>% plot(title="Break-Down for single obs with Fully Paid response")
```

```{r}
plot_fp1 = modelo_1_1_explained %>% predict_profile(new_observation = select(single_observation, -c('ID'))) %>% plot(title="Break-Down Fully Paid response",  variables=c("Annual.Income"))
plot_fp_2 = modelo_1_1_explained %>% predict_profile(new_observation = select(single_observation, -c('ID'))) %>% plot(title="Break-Down Fully Paid response",  variables=c("Credit.Score"))
plot_fp_3= modelo_1_1_explained %>% predict_profile(new_observation = select(single_observation, -c('ID'))) %>% plot(title="Break-Down Fully Paid response",  variables=c("Current.Loan.Amount"))
plot_fp_4= modelo_1_1_explained %>% predict_profile(new_observation = select(single_observation, -c('ID'))) %>% plot(title="Break-Down Fully Paid response",  variables=c("Monthly.Debt"))
```

```{r}
plot_fp1
```

```{r}
plot_fp_2
```

```{r}
plot_fp_3
#510 y 260
```

```{r}
plot_fp_4
```

Charged off

```{r}
single_observation = Train[11434, ]
modelo_1_1_explained %>% predict(single_observation)
modelo_1_1_explained %>% predict(single_observation)
modelo_1_1_explained %>% predict_parts(new_observation = single_observation) %>% plot(title="Break-Down for single obs with Charged Off response")
```

```{r}
plot_cf1 = modelo_1_1_explained %>% predict_profile(new_observation = select(single_observation, -c('ID'))) %>% plot(title="Break-Down for single obs with Charged Off response",  variables=c("Annual.Income"))
plot_cf_2 = modelo_1_1_explained %>% predict_profile(new_observation = select(single_observation, -c('ID'))) %>% plot(title="Break-Down for single obs with Charged Off response",  variables=c("Credit.Score"))
plot_cf_3= modelo_1_1_explained %>% predict_profile(new_observation = select(single_observation, -c('ID'))) %>% plot(title="Break-Down for single obs with Charged Off response",  variables=c("Current.Loan.Amount"))
plot_cf_4= modelo_1_1_explained %>% predict_profile(new_observation = select(single_observation, -c('ID'))) %>% plot(title="Break-Down for single obs with Charged Off response",  variables=c("Monthly.Debt"))
```


```{r}
plot_cf1
```
```{r}
plot_cf_2
```

```{r}
plot_cf_3
```

```{r}
plot_cf_4
```

